---
title: "Developing Data Products: Shiny Application and Reproducible Pitch"
author: "Joshua Paolo Acilo"
date: "August 8, 2019"
output: slidy_presentation      
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(dplyr)
```

## Task

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

The application must include the following

1. Some form of input (widget: textbox, radio button, checkbox, ...)
2. Some operation on the ui input in sever.R
3. Some reactive output displayed as a result of server calculations
4. You must also include enough documentation so that a novice user could use your application.
5. The documentation should be at the Shiny website itself. Do not post to an external link.

## Motivation

This web application is built to study the k means clustering procedure in the mtcars dataset. The user specifies the x and y variables which defines the scatterplot. The user can vary the number of clusters for the k means procedure in order to find similar patterns in the dataset, a way of exploring the subtle bivariate commonalities present among the features in the given data.

## 1974 Motor Trend US Dataset

This dataset comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

What kind of data are we dealing with?

```{r}
mtcars %>% str()
```


## The App

```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(shiny)

ui <- fluidPage(pageWithSidebar(
        headerPanel('K-Means Clustering x 1974 Motor Trend US Dataset'),
        sidebarPanel(
                selectInput('xcol', 'x-variable?', names(mtcars)),
                selectInput('ycol', 'y-variable?', names(mtcars),
                            selected = names(mtcars)[[2]]),
                numericInput('clusters', 'how many clusters?', 3,
                             min = 1, max = 12)
        ),
        mainPanel(
                plotOutput('plot_me')
        )
))

server <- function(input, output, session) {
        
        selectedData <- reactive({
                mtcars[, c(input$xcol, input$ycol)]
        })
        
        clusters <- reactive({
                kmeans(selectedData(), input$clusters)
        })
        
        output$plot_me <- renderPlot({
                palette(c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3",
                          "#FF7F00", "#FFFF33", "#A65628", "#F781BF", "#999999"))
                
                par(mar = c(5.1, 4.1, 0, 1))
                plot(selectedData(),
                     col = clusters()$cluster,
                     pch = 20, cex = 3)
                points(clusters()$centers, pch = 4, cex = 4, lwd = 4)
        })
        
}

shinyApp(ui = ui, server = server)

```
